---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: Arial, sans-serif;
  background-color: #f9fbfd;
  color: #222222;
  line-height: 1.6;
  padding: 20px;
}

h2 {
  color: #1f4e79;
  border-bottom: 2px solid #1f4e79;
  padding-bottom: 6px;
}

h3 {
  color: #0b5394;
}

p {
  font-size: 16px;
}
```


## Tracking ad engagement patterns

This report analyses responses collected about ad type, interest level, clicks, and the time the ad was seen.

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTb4rR1s1h0Mr-yIQi2uQkB5QRxBCqUDA53fMHmO0kqXEurtaEqvVDd3xU0MIuYyQ0YPD0C9AAmGCRe/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    type = `What type of ad is this?`,
    interest = `How interested are you in this ad? (1-10)`,
    click = `Did you click on the ad?`,
    time = `What time did you see this ad?`
  )
```

```{r}
total_ads <- nrow(latest_data)
mean_interest <- mean(latest_data$interest, na.rm = TRUE)
max_interest <- max(latest_data$interest, na.rm = TRUE)
```
There are currently **`r total_ads`** responses in this dataset.

The average interest score is **`r round(mean_interest, 2)`** out of 10.

The highest interest score recorded is **`r max_interest`**.

This indicates that overall interest in the ads is relatively low.

### Ad type distribution

This bar chart shows the distribution of ad types.
Clothing ads are the most common, while technology ads appear the least frequently.
```{r}
ggplot(latest_data, aes(x = type)) +
  geom_bar() +
  labs(
    title = "Distribution of Ad Types",
    x = "Ad type",
    y = "Count"
  )
```
### Ad click distribution

This bar chart shows whether people clicked on the ad.
Most responses were "no", suggesting low engagement with the ads.
```{r}
ggplot(latest_data, aes(x = click)) +
  geom_bar() +
  labs(
    title = "Ad Click Distribution",
    x = "Clicked on ad",
    y = "Count"
  )
```


